animbook: Visualizing changes in performance measures and demographic affiliations using animation

### 2023-10-29 animbook-journal.Rmd
4th version of the paper

---
title: "animbook: Visualizing changes in performance measures and demographic affiliations using animation"
abstract: >
  Categorical data has often been presented statically despite its potential to unveil an intriguing movement pattern relevant to the various domains of data, including company ranking quantile in the accounting data and shifts in voter party affiliations. Inspired by the animation in the New York Times article "Extensive data show punishing reach of racism for black boys," this paper aims to develop an R package, animbook, that can generalize the animation to suitably apply to a wider range of data. The package included a function that allowed for the transformation of the data and connection with elements of the plot that would be animated. This results in an animation tool that helps communicate complex data, enhancing the narrative and keeping it engaged for the general audience. 
draft: true
author:  
  - name: Krisanat Anukarnsakulchularp
    affiliation: Monash University
    address:
    - Department of Econometrics and Business Statistics
    - Melbourne, Australia
    orcid: 0009-0008-5638-7124
    email:  kanu0003@student.monash.edu
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: animbook-journal.bib
---

@@

The concept of "zombie companies" began to attract attention when @zombie_companies_2008 reported on their proliferation in Japan. Zombie companies are those with an interest coverage ratio of less than one for a period of more than three years, that is, companies taking space in the market but adding no life to the economy. We would detect their presence by a drop in performance, which is a movement pattern in their relative ranking over time. Generally, studying movement patterns is interesting for many problems, including rocket ship startups that rapidly perform well, or in politics, to study voters who switch party affiliation between elections. Viewing changes between categories over time is an interesting challenge for visualization.

The New York Times provided a possible solution in the article titled "Extensive data show punishing reach of racism for black boys" (@the_new_york_time) to tell the story of how racism appears to inhibit socioeconomic change. This animation is the motivation for the new visualization presented here, to be applied generally.

The challenge in producing an animation like that in New York Times article animation is the transformation of the data, and connection with elements of the plot that will be animated. The complexities include standardizing starting times of the temporal variable, allowing for the user to choose the number of categories, standardizing distributions and allowing the user to input pre-computed categorical data. These considerations provide the objective for creating an R package that can generalize the animation to suitably apply to a wide range of data.

The structure of this paper is as follows. The next section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies. The next section describes the expected data format. Following this is an explanation of available animation tools, and how they are employed for this problem. A section on the functions of the package and how the visualization is designed, demonstrates how the data is mapped to the animation. The last two sections illustrate the usage of the package and applications to company performance and changing political allegiance.

@@

```{r nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package..", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
knitr::include_graphics("figures/NYT.png")
```

@@

  The paths of observations need to be interpolated to create small changes in the position of points to produce the appearance of motion, as mentioned in the Animation tools section. These interpolate functions in \CRANpkg{gganimate} and \CRANpkg{plotly} only generate a linear path between points. However, linear paths are visually less appealing than non-linear paths.  <!-- Non-linear curves like the sigmoid curves are considered instead, as they provide a better display of proportions.--> Sigmoid curves are commonly used in Sankey diagrams, however, @Shaffer_2019 argues that a sine curve more accurately represents proportion throughout the path. This is illustrated in Figure \@ref(fig:proportional-shade). The sigmoid accurately represents the proportion at the beginning and end, as it curves, the shape gets narrower, leading to less accurate proportion representation than the sine curve.

@@

p2 <- anim_animate(p)
kan_p2 <- anim_animate(kan_p)
```

@@

``` r
gganimate::animate(p2)

gganimate::animate(kan_p2)
```

```{r osiris-figure, fig.cap = "The wallaby plot  visualization shows the companies that exited the market. There are more United States companies that fall down into a not listed group compared to Japanese companies.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
knitr::include_graphics("figures/animation-exit.png")
```

```{r osiris-gif, out.extra="class = 'gif'", fig.cap = "The wallaby plot visualization shows the companies that exited the market. There are more United States companies that fall down into a not listed group compared to Japanese companies.", eval=knitr::is_html_output()}
knitr::include_graphics("figures/exit.gif")
```

```{r kan-osiris-figure, fig.cap = "The kangaroo plot visualization shows the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018, for a sample of data extracted from the Osiris database. The 'not listed' category indicates companies not yet listed, or removed from the listing. Most companies stay in the same quantile group, with a small number moving up and down. Most of the movement is made by American companies, which supports the OECD report.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
knitr::include_graphics("figures/osiris.png")
```

```{r kan-osiris-gif, out.extra="class = 'gif'", fig.cap = "The kangaroo plot visualization shows the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018, for a sample of data extracted from the Osiris database. The 'not listed' category indicates companies not yet listed, or removed from the listing. Most companies stay in the same quantile group, with a small number moving up and down. Most of the movement is made by American companies, which supports the OECD report.", eval=knitr::is_html_output()}
knitr::include_graphics("figures/kan-osiris.gif")
```

  From the plot, a higher proportion of US companies have exited the market, confirming the OECD report (@oecd_report) that the United States has a higher turnover rate than Japan. An interesting finding is that all of the top 25% of companies that exited the market are only from the United States. It may be due to the absence of Japanese companies in the Top 25% in 2006, or it could be that Japanese companies who started in the Top 25% in 2006 were not delisted. Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:kan-osiris-figure}','\\@ref(fig:kan-osiris-gif)'))`, confirmed that there are non-Japanese companies that start at the Top 25% in 2006.

@@

The Australian Election Study data was collected from ADA Dataverse (@aeles). The dataset included in the \pkg{animbook} package contains 1,468 rows and 4 variables of information: ID, year, party, and gender. This dataset comprises survey responses from the 2019 election. The year column was transformed from the two different questions to answer how the top party performs in keeping the old voters for different genders, relative to the 2016 Australian election results.

@@

p_voter <- wallaby_plot(object = voter,
                  group_palette = RColorBrewer::brewer.pal(9, "Set1"),
                  shade_palette = c("#737373", "#969696", "#BDBDBD",
                                    "#D9D9D9","#D9D9D9","#D9D9D9"),
                  rendering = "ggplot",
                  subset = "top",
                  relation = "one_many",
                  height = 1,
                  size = 2,
                  width = 100,
                  total_point = 1000)

@@

```{r voter-figure, fig.cap = "The wallaby plot visualization shows how does the top party perform in keeping the old voters for different genders. Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
knitr::include_graphics("figures/animation-voter.png")
```

```{r voter-gif, out.extra="class = 'gif'", fig.cap = "The wallaby plot visualization shows how does the top party perform in keeping the old  voters for different genders. Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.", eval=knitr::is_html_output()}
knitr::include_graphics("figures/voter.gif")
```

From Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:voter-figure}','\\@ref(fig:voter-gif)'))`, it is clear that individuals who identified their gender as 'others' shifted their votes from the Liberal, the leading party in 2016, to the Greens party. These changes could be due to the Green Party's "A FAIRER, MORE EQUAL COMMUNITY" campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals. If the Liberal Party wishes to retain this demographic of voters, they may need to consider implementing a campaign focused on LGBTIQ+ issues.

>>>>

---
title: "animbook: Visualizing changes in performance measures and demographic affiliations using animation"
abstract: >
  Categorical data has often been presented statically despite its potential to unveil an intriguing movement pattern relevant to the various domains of data, including company ranking quantile in the accounting data and shifts in voter party affiliations. Inspired by the animation in the New York Times article "Extensive data show punishing reach of racism for black boys," this paper aims to develop an R package, animbook, that can generalize the animation to suitably apply to a wider range of data. The package included a function that allowed for the transformation of the data and connection with elements of the plot that would be animated. This results in an animation tool that helps communicate complex data, enhancing the narrative and keeping it engaged for the general audience. 
draft: true
author:  
  - name: Krisanat Anukarnsakulchularp
    affiliation: Monash University
    address:
    - Department of Econometrics and Business Statistics
    - Melbourne, Australia
    orcid: 0009-0008-5638-7124
    email:  kanu0003@student.monash.edu
  - name: Dianne Cook
    affiliation: Monash University 
    address: 
      - Department of Econometrics and Business Statistics
      - Melbourne, Australia
    email: dicook@monash.edu
    orcid: 0000-0002-3813-7155
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: animbook-journal.bib
---

@@

The concept of "zombie companies" began to attract attention when @zombie_companies_2008 reported on their proliferation in Japan. Zombie companies are those with an interest coverage ratio of less than one for a period of more than three years, that is, companies taking space in the market but adding no life to the economy. We would detect their presence by a drop in performance, which is a movement pattern in their relative ranking over time. Generally, studying movement patterns is interesting for many problems, including rocket ship start-ups that rapidly perform well or in politics, to study voters who switch party affiliation between elections. Viewing changes between categories over time is an interesting challenge for visualization.

  The New York Times provided a possible solution in the article titled "Extensive data show punishing reach of racism for black boys" (@the_new_york_time) to tell the story of how racism appears to inhibit socioeconomic change. This animation is the motivation for the new visualization presented here to be applied generally.

  The challenge in producing an animation like that in the New York Times article animation is the transformation of the data and connection with elements of the plot that will be animated. The complexities include allowing the user to choose the number of categories, standardizing distributions, and allowing the user to input pre-computed categorical data. These considerations provide the objective for creating an R package that can generalize the animation to suitably apply to a wide range of data.

  The structure of this paper is as follows. The next section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies. The next section describes the expected data format. Following this is an explanation of available animation tools and how they are employed for this problem. A section on the functions of the package and how the visualization is designed demonstrates how the data is mapped to the animation. The last two sections illustrate the usage of the package and applications to company performance and changing political allegiance.

@@

```{r nyt, fig.cap="Screenshot of the New York Times animation, which is the motivation for this visualization package.", fig.width=8, fig.align='center', out.width="100%", layout = "l-body"}
knitr::include_graphics("figures/NYT.png")
```

@@

  The paths of observations need to be interpolated to create small changes in the position of points to produce the appearance of motion, as mentioned in the Animation tools section. These interpolate functions in \CRANpkg{gganimate} and \CRANpkg{plotly} only generate a linear path between points. However, linear paths are visually less appealing than non-linear paths. Sigmoid curves are commonly used in Sankey diagrams (@Hvitfeldt_2018). However, @Shaffer_2019 argues that a sine curve more accurately represents proportion throughout the path. This is illustrated in Figure \@ref(fig:proportional-shade). The sigmoid accurately represents the proportion at the beginning and end, but as it curves, the shape gets narrower, leading to a less accurate proportion representation than the sine curve.

@@

kan_p2 <- anim_animate(kan_p)

p2 <- anim_animate(p)
```

@@

``` r
gganimate::animate(kan_p2)

gganimate::animate(p2)
```

```{r kan-osiris-figure, fig.cap = "The kangaroo plot visualization shows the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018 for a sample of data extracted from the Osiris database. The 'not listed' category indicates companies not yet listed or removed from the listing. Most companies stay in the same quantile group, with a small number moving up and down. Most of the movement is made by American companies, which supports the OECD report.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
knitr::include_graphics("figures/osiris.png")
```

```{r kan-osiris-gif, out.extra="class = 'gif'", fig.cap = "The kangaroo plot visualization shows the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018 for a sample of data extracted from the Osiris database. The 'not listed' category indicates companies not yet listed or removed from the listing. Most companies stay in the same quantile group, with a small number moving up and down. Most of the movement is made by American companies, which supports the OECD report.", eval=knitr::is_html_output()}
knitr::include_graphics("figures/kan-osiris.gif")
```

```{r osiris-figure, fig.cap = "The wallaby plot visualization shows the companies that exited the market. There are more United States companies that fall down into a not listed group (got de-listed) compared to Japanese companies.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
knitr::include_graphics("figures/animation-exit.png")
```

```{r osiris-gif, out.extra="class = 'gif'", fig.cap = "The wallaby plot visualization shows the companies that exited the market. There are more United States companies that fall down into a not listed group (got de-listed) compared to Japanese companies.", eval=knitr::is_html_output()}
knitr::include_graphics("figures/exit.gif")
```

  From the kangaroo plot (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:kan-osiris-figure}','\\@ref(fig:kan-osiris-gif)'))`), most companies are staying in the same quantile group, with only a small number moving upward or downward. Most of the movement is made by American companies, supporting the OECD report (@oecd_report) that the United States has a higher turnover rate compared to Japan. To emphasize this point, the wallaby plot can be utilized (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`), this reinforces that there are more American companies de-listed compared to Japanese companies. There could be various reasons for this trend, such as the absence of Japanese companies in the Top 25% in 2006 or the possibility that Japanese companies who started in the Top 25% in 2006 were not de-listed.

@@

The Australian Election Study data was collected from ADA Dataverse (@aeles). The dataset included in the \pkg{animbook} package contains 1,468 rows and 4 variables of information: ID, year, party, and gender. This dataset comprises survey responses from the 2019 election. The year column was transformed from the two different questions to answer how the top party performs in keeping the old voters for different genders relative to the 2016 Australian election results.

@@

p_voter <- wallaby_plot(object = voter,
                  group_palette = c("pink", "blue", "red"),
                  shade_palette = c("#737373", "#969696", "#BDBDBD",
                                    "#D9D9D9","#D9D9D9","#D9D9D9"),
                  rendering = "ggplot",
                  subset = "top",
                  relation = "one_many",
                  height = 1,
                  size = 2.5,
                  width = 100,
                  total_point = 1000)

@@

```{r voter-figure, fig.cap = "The wallaby plot visualization shows how the top party performs in keeping the old voters of different genders. Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party. Interestingly, individual who identified as others overwhelmingly shifted their party affiliations to the Greens party.", fig.width=8, fig.align='center', out.width="100%", layout = "l-page", eval=knitr::is_latex_output()}
knitr::include_graphics("figures/animation-voter.png")
```

```{r voter-gif, out.extra="class = 'gif'", fig.cap = "The wallaby plot visualization shows how the top party performs in keeping the old voters of different genders. Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party. Interestingly, individual who identified as others overwhelmingly shifted their party affiliations to the Greens party.", eval=knitr::is_html_output()}
knitr::include_graphics("figures/voter.gif")
```

  From Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:voter-figure}','\\@ref(fig:voter-gif)'))`, it reveals an intriguing pattern where individuals who identified their gender as 'others' have shifted their voting preference from the Liberal Party, the leading party in 2006, to the Greens Party. This change in behavior could be linked to the Green Party's "A FAIRER, MORE EQUAL COMMUNITY" campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals.

  Liberal Party analysts may find it worthwhile to delve into this topic further, considering both the benefits and drawbacks. If the Liberal Party wishes to retain this demographic of voters, they may need to consider implementing a campaign focused on LGBTIQ+ issues. However, this may also lead to a further defection of conservative voters.

### 2023-10-29 animbook-journal.tex
4th version of the paper

% !TeX root = RJwrapper.tex
\title{animbook: Visualizing changes in performance measures and demographic affiliations using animation}
\author{by Krisanat Anukarnsakulchularp}

@@

The concept of ``zombie companies'' began to attract attention when Caballero, Hoshi, and Kashyap (2008) reported on their proliferation in Japan. Zombie companies are those with an interest coverage ratio of less than one for a period of more than three years, that is, companies taking space in the market but adding no life to the economy. We would detect their presence by a drop in performance, which is a movement pattern in their relative ranking over time. Generally, studying movement patterns is interesting for many problems, including rocket ship startups that rapidly perform well, or in politics, to study voters who switch party affiliation between elections. Viewing changes between categories over time is an interesting challenge for visualization.

The New York Times provided a possible solution in the article titled ``Extensive data show punishing reach of racism for black boys'' (Badger et al. (2018)) to tell the story of how racism appears to inhibit socioeconomic change. This animation is the motivation for the new visualization presented here, to be applied generally.

The challenge in producing an animation like that in New York Times article animation is the transformation of the data, and connection with elements of the plot that will be animated. The complexities include standardizing starting times of the temporal variable, allowing for the user to choose the number of categories, standardizing distributions and allowing the user to input pre-computed categorical data. These considerations provide the objective for creating an R package that can generalize the animation to suitably apply to a wide range of data.

The structure of this paper is as follows. The next section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies. The next section describes the expected data format. Following this is an explanation of available animation tools, and how they are employed for this problem. A section on the functions of the package and how the visualization is designed, demonstrates how the data is mapped to the animation. The last two sections illustrate the usage of the package and applications to company performance and changing political allegiance.

@@

\caption{Screenshot of the New York Times animation, which is the motivation for this visualization package..}\label{fig:nyt}
\end{figure}

@@

The animated visualization can be an effective communication tool (R. E. Mayer and Moreno (2002); Robertson et al. (2008)). It helps with communicating complex data, enhancing the narrative, and keeping it engaged for the audience. According to R. E. Mayer and Moreno (2002), animation can improve learning, especially when the goal is to promote deep understanding.

@@

As mentioned in the Animation tools section, the paths of observations are getting interpolated. These functions only generate a linear path between points. However, linear paths may not be suitable for creating proportional shading, as they do not accurately represent the proportions. Non-linear curves like the sigmoid curves should be considered instead, as they provide a better display of proportions. These curves are commonly used in multiple Sankey diagrams, but there is a limitation on this shape. The issue is shown in Figure \ref{fig:proportional-shade}. While it does accurately represent the proportion at the beginning and end, as it curves, the shape gets narrower, leading to less accurate proportion representation (Shaffer (2019))

@@

\begin{verbatim}
#> # A tibble: 10 x 5
#>    id     time qtile frame color
#>    <fct> <int> <dbl> <dbl> <fct>
#>  1 1      2020     5    33 X    
#>  2 1      2023     5    34 X    
#>  3 2      2020     5     5 X    
#>  4 2      2023     5     6 X    
#>  5 3      2020     5    48 X    
#>  6 3      2023     5    49 X    
#>  7 4      2020     5    33 X    
#>  8 4      2023     5    34 X    
#>  9 5      2020     5     3 X    
#> 10 5      2023     5     4 X
\end{verbatim}

@@

\begin{verbatim}
#> List of 2
#>  $ data    : tibble [400 x 5] (S3: tbl_df/tbl/data.frame)
#>   ..$ id   : Factor w/ 200 levels "1","2","3","4",..: 1 1 2 2 3 3 4 4 5 5 ...
#>   ..$ time : int [1:400] 2020 2023 2020 2023 2020 2023 2020 2023 2020 2023 ...
#>   ..$ qtile: num [1:400] 5 5 5 5 5 5 5 5 5 5 ...
#>   ..$ frame: num [1:400] 33 34 5 6 48 49 33 34 3 4 ...
#>   ..$ color: Factor w/ 2 levels "X","Y": 1 1 1 1 1 1 1 1 1 1 ...
#>  $ settings:List of 7
#>   ..$ gap           : num 0.1
#>   ..$ xbreaks       : int [1:2] 2020 2023
#>   ..$ label         : chr [1:5] "A" "B" "C" "D" ...
#>   ..$ order         : chr [1:5] "A" "B" "C" "D" ...
#>   ..$ time_dependent: logi FALSE
#>   ..$ runif_min     : num 1
#>   ..$ runif_max     : num 50
#>  - attr(*, "class")= chr "animbook"
\end{verbatim}

@@

The accounting Osiris data that will be used in this section was collected from Bureau van Dijk ({``Osiris''} (n.d.)). This data set comprises 30,000 rows and 94 variables of information on listed and major unlisted/delisted companies worldwide. The only variables of interest from this data set are ID, year, country, and sales. A subset version of this data set, which only contained variables of interest from 2006 to 2018, is included in this package.

As mentioned in the OECD report (McGowan, Andrews, and Millot (2017)), the United States has a faster metabolize rate relative to Japan company. An animation will be created using the \texttt{animbook} package to enhance communication with data. First, filter the countries to include only the United States and Japan. Then, prepare the Osiris data using the \texttt{anim\_prep} function with the first scaling, which is a ranking method. Next, use the \texttt{wallaby\_plot} function to create a \texttt{ggplot} object and add default settings for \texttt{gganimate} rendering.

@@

p2 <- anim_animate(p)
kan_p2 <- anim_animate(kan_p)
\end{verbatim}

\begin{verbatim}
gganimate::animate(p2)

gganimate::animate(kan_p2)
\end{verbatim}

@@

\caption{The animate visualization shows the companies that exited the market. There are more United States companies that fall down into a not listed group compared to Japanese companies.}\label{fig:osiris-figure}
\end{figure}

\caption{The animate visualization shows the movement of the companies between the groups from 2006 to 2018. In 2006, there were no Japanese companies in the Top 25\% group.}\label{fig:kan-osiris-figure}
\end{figure}

From the plot, a higher proportion of US companies have exited the market, confirming the OECD report (McGowan, Andrews, and Millot (2017)) that the United States has a higher turnover rate than Japan. An interesting finding is that all of the top 25\% of companies that exited the market are only from the United States. It may be due to the absence of Japanese companies in the Top 25\% in 2006, or it could be that Japanese companies who started in the Top 25\% in 2006 did not delist. Figure \ref{fig:kan-osiris-figure}, confirmed that there are non-Japanese companies that start at the Top 25\% in 2006.

@@

The Australian Election Study data was collected from ADA Dataverse (McAllister et al. (2023)). The dataset included in the \pkg{animbook} package contains 1,468 rows and 4 variables of information: ID, year, party, and gender. This dataset comprises survey responses from the 2019 election. The year column was transformed from the two different questions to answer the question, based on the 2016 Australian election results, how the top party performs in keeping the old voters for different genders.

@@

\caption{The animate visualization shows how does the top party perform in keeping the old voters for different genders. Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party.}\label{fig:voter-figure}
\end{figure}

From Figure \ref{fig:voter-figure}, it is clear that individuals who identified their gender as `others' shifted their votes from the Liberal, the leading party in 2016, to the Greens party. These changes could be due to the Green Party's ``A FAIRER, MORE EQUAL COMMUNITY'' campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals. If the Liberal Party wishes to retain this demographic of voters, they may need to consider implementing a campaign focused on LGBTIQ+ issues.

@@

I also acknowledge the use of ChatGPT (\url{https://chat.openai.com/}) to paraphrase the sentence.

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-bvd}{}}%
{``Osiris.''} n.d. \emph{Bvd}. Bureau van Dijk. \url{https://www.bvdinfo.com/en-gb/our-products/data/international/osiris}.

@@

>>>>

% !TeX root = RJwrapper.tex
\title{animbook: Visualizing changes in performance measures and demographic affiliations using animation}
\author{by Krisanat Anukarnsakulchularp and Dianne Cook}

@@

The concept of ``zombie companies'' began to attract attention when Caballero, Hoshi, and Kashyap (2008) reported on their proliferation in Japan. Zombie companies are those with an interest coverage ratio of less than one for a period of more than three years, that is, companies taking space in the market but adding no life to the economy. We would detect their presence by a drop in performance, which is a movement pattern in their relative ranking over time. Generally, studying movement patterns is interesting for many problems, including rocket ship start-ups that rapidly perform well or in politics, to study voters who switch party affiliation between elections. Viewing changes between categories over time is an interesting challenge for visualization.

The New York Times provided a possible solution in the article titled ``Extensive data show punishing reach of racism for black boys'' (Badger et al. (2018)) to tell the story of how racism appears to inhibit socioeconomic change. This animation is the motivation for the new visualization presented here to be applied generally.

The challenge in producing an animation like that in the New York Times article animation is the transformation of the data and connection with elements of the plot that will be animated. The complexities include allowing the user to choose the number of categories, standardizing distributions, and allowing the user to input pre-computed categorical data. These considerations provide the objective for creating an R package that can generalize the animation to suitably apply to a wide range of data.

The structure of this paper is as follows. The next section explains the animation in The New York Times article and why it is relevant to the problem of studying zombie companies. The next section describes the expected data format. Following this is an explanation of available animation tools and how they are employed for this problem. A section on the functions of the package and how the visualization is designed demonstrates how the data is mapped to the animation. The last two sections illustrate the usage of the package and applications to company performance and changing political allegiance.

@@

\caption{Screenshot of the New York Times animation, which is the motivation for this visualization package.}\label{fig:nyt}
\end{figure}

@@

The animated visualization can be an effective communication tool (R. E. Mayer and Moreno (2002); Robertson et al. (2008)). It helps with communicating changing data values, enhancing the narrative, and keeping it engaging for the audience. According to R. E. Mayer and Moreno (2002), animation can improve learning, especially when the goal is to promote deep understanding.

@@

The paths of observations need to be interpolated to create small changes in the position of points to produce the appearance of motion, as mentioned in the Animation tools section. These interpolate functions in \CRANpkg{gganimate} and \CRANpkg{plotly} only generate a linear path between points. However, linear paths are visually less appealing than non-linear paths. Sigmoid curves are commonly used in Sankey diagrams (Hvitfeldt (2018)). However, Shaffer (2019) argues that a sine curve more accurately represents proportion throughout the path. This is illustrated in Figure \ref{fig:proportional-shade}. The sigmoid accurately represents the proportion at the beginning and end, but as it curves, the shape gets narrower, leading to a less accurate proportion representation than the sine curve.

@@

\begin{verbatim}
#> # A tibble: 10 x 5
#>    id     time qtile frame color
#>    <fct> <int> <dbl> <dbl> <fct>
#>  1 1      2020     5    11 X    
#>  2 1      2023     5    12 X    
#>  3 2      2020     5    39 X    
#>  4 2      2023     5    40 X    
#>  5 3      2020     5     3 X    
#>  6 3      2023     5     4 X    
#>  7 4      2020     5    12 X    
#>  8 4      2023     5    13 X    
#>  9 5      2020     5    46 X    
#> 10 5      2023     5    47 X
\end{verbatim}

@@

\begin{verbatim}
#> List of 2
#>  $ data    : tibble [400 x 5] (S3: tbl_df/tbl/data.frame)
#>   ..$ id   : Factor w/ 200 levels "1","2","3","4",..: 1 1 2 2 3 3 4 4 5 5 ...
#>   ..$ time : int [1:400] 2020 2023 2020 2023 2020 2023 2020 2023 2020 2023 ...
#>   ..$ qtile: num [1:400] 5 5 5 5 5 5 5 5 5 5 ...
#>   ..$ frame: num [1:400] 11 12 39 40 3 4 12 13 46 47 ...
#>   ..$ color: Factor w/ 2 levels "X","Y": 1 1 1 1 1 1 1 1 1 1 ...
#>  $ settings:List of 7
#>   ..$ gap           : num 0.1
#>   ..$ xbreaks       : int [1:2] 2020 2023
#>   ..$ label         : chr [1:5] "A" "B" "C" "D" ...
#>   ..$ order         : chr [1:5] "A" "B" "C" "D" ...
#>   ..$ time_dependent: logi FALSE
#>   ..$ runif_min     : num 1
#>   ..$ runif_max     : num 50
#>  - attr(*, "class")= chr "animbook"
\end{verbatim}

@@

The accounting Osiris data that will be used in this section was collected from Bureau van Dijk ({``Osiris''} (2023)). This data set comprises 30,000 rows and 94 variables of information on listed and major unlisted/delisted companies worldwide. The variables of interest from this data set are ID, year, country, and sales. A subset of companies from this data set is used recorded from 2006 to 2018. This sample is included in the package.

An OECD report (McGowan, Andrews, and Millot (2017)) claims that the United States has a faster metabolic rate relative to Japanese companies. We use the wallaby plot and kangaroo plot animation to explore this. The steps are:

\begin{itemize}
\tightlist
\item
  Filter the countries to include only the United States and Japan.
\item
  Prepare the data using the \texttt{anim\_prep} function with the first scaling, which is a ranking method.
\item
  Use the \texttt{wallaby\_plot} and \texttt{kangaroo\_plot} functions to create \texttt{ggplot} objects and add default settings for \texttt{gganimate} rendering.
\end{itemize}

@@

kan_p2 <- anim_animate(kan_p)

p2 <- anim_animate(p)
\end{verbatim}

\begin{verbatim}
gganimate::animate(kan_p2)

\caption{The kangaroo plot visualization shows the movement of the Japanese and US companies between the performance sales quantiles from 2006 to 2018 for a sample of data extracted from the Osiris database. The 'not listed' category indicates companies not yet listed or removed from the listing. Most companies stay in the same quantile group, with a small number moving up and down. Most of the movement is made by American companies, which supports the OECD report.}\label{fig:kan-osiris-figure}
\end{figure}

@@

\caption{The wallaby plot visualization shows the companies that exited the market. There are more United States companies that fall down into a not listed group (got de-listed) compared to Japanese companies.}\label{fig:osiris-figure}
\end{figure}

From the kangaroo plot (Figure \ref{fig:kan-osiris-figure}), most companies are staying in the same quantile group, with only a small number moving upward or downward. Most of the movement is made by American companies, supporting the OECD report (McGowan, Andrews, and Millot (2017)) that the United States has a higher turnover rate compared to Japan. To emphasize this point, the wallaby plot can be utilized (Figure \ref{fig:osiris-figure}), this reinforces that there are more American companies de-listed compared to Japanese companies. There could be various reasons for this trend, such as the absence of Japanese companies in the Top 25\% in 2006 or the possibility that Japanese companies who started in the Top 25\% in 2006 were not de-listed.

@@

The Australian Election Study data was collected from ADA Dataverse (McAllister et al. (2023)). The dataset included in the \pkg{animbook} package contains 1,468 rows and 4 variables of information: ID, year, party, and gender. This dataset comprises survey responses from the 2019 election. The year column was transformed from the two different questions to answer how the top party performs in keeping the old voters for different genders relative to the 2016 Australian election results.

@@

\caption{The wallaby plot visualization shows how the top party performs in keeping the old voters of different genders. Most voters remain loyal to the party, but a small fraction of voters with roughly equal male-to-female ratio switch primarily to the other major party. Interestingly, individual who identified as others overwhelmingly shifted their party affiliations to the Greens party.}\label{fig:voter-figure}
\end{figure}

From Figure \ref{fig:voter-figure}, it reveals an intriguing pattern where individuals who identified their gender as `others' have shifted their voting preference from the Liberal Party, the leading party in 2006, to the Greens Party. This change in behavior could be linked to the Green Party's ``A FAIRER, MORE EQUAL COMMUNITY'' campaign, which advocates for full equality under the law and communities for LGBTIQ+ individuals.

Liberal Party analysts may find it worthwhile to delve into this topic further, considering both the benefits and drawbacks. If the Liberal Party wishes to retain this demographic of voters, they may need to consider implementing a campaign focused on LGBTIQ+ issues. However, this may also lead to a further defection of conservative voters.

@@

I also acknowledge the use of ChatGPT (\url{https://chat.openai.com/}) to improve the text, grammar and spelling.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Hvitfeldt_2018}{}}%
Hvitfeldt, Emil. 2018. {``Recreate - Sankey Flow Chart.''} \emph{Recreate - Sankey Flow Chart}. \url{https://emilhvitfeldt.com/post/2018-03-20-recreate-sankey-flow-chart/}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-bvd}{}}%
{``Osiris.''} 2023. \emph{Bvd}. Bureau van Dijk. \url{https://www.bvdinfo.com/en-gb/our-products/data/international/osiris}.

@@

\address{%
Dianne Cook\\
Monash University\\%
Department of Econometrics and Business Statistics\\ Melbourne, Australia\\
%
%
\textit{ORCiD: \href{https://orcid.org/0000-0002-3813-7155}{0000-0002-3813-7155}}\\%
\href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}%
}
